Barneby Lives!

### 2023-05-10 scripts/taxonomy_setup.Rmd
function to retrieve found results from powo

```{r}
library(tidyverse)
library(kewr)
```

@@

```{r}
re <- search_powo("Ivesia lycopodioides")

# some considerations....

# If the species cannot be found, RESULTS will be NULL 
search_powo("Ivesia lycopodioides var. lycopodioides")
# if results are NULL, can we strip from subsp./var./ssp. until the end to query only species?

@@

re1 <- re[['results']]

@@

data("WFO.example")

WFO.remember()

>>>>

```{r}
library(tidyverse)
library(kewr)
library(WorldFlora)
WFO.remember()
```

@@

```{r}
x <- search_powo("Ivesia lycopodioides")
# some considerations....

# If the species cannot be found, RESULTS will be NULL 
re_none <- search_powo("Ivesia lycopodioides var. lycopodioides")

try_again <-

is.null(re_none[["results"]]){

  try_again

} else {final <- result_grabber(query_results)}

# if results are NULL, can we strip from subsp./var./ssp. until the end to query only species?

@@

# once everything has gone correctly - i.e. we have found the species, we come to
# this stage of the process where we extract the values.

result_grabber <- function(x){

  # subset the appropriate data frame, there is one if clean data were entered, 
  # and two if a synonym was entered.
  results <- x[['results']]
  resultT <- data.frame(results[which(lapply(results, length) == 8)])

  # the main variables which all results should have. 
  family = resultT$family
  authority = resultT$author
  full_name = resultT$name
  split_name <- unlist(str_split(full_name, pattern = " "))
  genus = split_name[1]
  epithet = split_name[2]

  # the infra species information if relevant. 
  if( length(split_name) > 2){
     infraspecies = split_name[length(split_name)]
  } else {infraspecies = NA}

  if( length(split_name) > 2){
     infrarank = str_extract(full_name, ' var\\. | spp\\. | subsp\\. ') |>
       str_trim(side = 'both')
  } else {infrarank = NA}

  taxonomic_info <- data.frame(
    family, name_authority = paste(full_name, authority), 
    full_name, genus, epithet, infrarank, infraspecies, authority
  )

  return(taxonomic_info)
}

result_grabber(re_syn)

@@
